Dike experiment

### 2023-01-25 manuscript.Rmd
Update manuscript.Rmd

---
title: "Dike experiment"
author: Markus Bauer*, Jakob Huber, Johannes Kollmann
output:
  officedown::rdocx_document:
    reference_docx: StylesTemplate.docx
  #bookdown::word_document2:
    #global_numbering: true
csl: template-journal-of-vegetation-science.csl
bibliography: bibliography.bib
---

@@

Max 8000 words <!--# Remove -->

@@

```{r set-up, include = FALSE}
library(knitr)
library(bookdown)
library(officedown)
library(officer)
library(tidyverse)
library(flextable)
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  dpi = 50
  )
set_flextable_defaults(
  font.family = "Times New Roman",
  font.size = 11
  )

# read analysis
#rmarkdown::render(here::here("results", "scripts", "Models.Rmd"), quiet = TRUE) # quiet to not get text from rendering
```

@@

Mischprobe aus mehreren Plots. Measured in \< 2mm fraction <!--# Write full description -->

```{r table-substrate, tab.id = "substrate", tab.cap = "Substrate"}
read_csv(here::here("data", "raw", "data_raw_table_1.csv")) %>%
  slice(-1) %>%
  qflextable() %>%
  bold(part = "header") %>%
  add_header_row(
    top = FALSE,
    values = read_csv(here::here("data", "raw", "data_raw_table_1.csv")) %>% slice(1)
    ) %>%
  autofit()
```

>>>>

---
title: "Dike experiment"
author: Markus Bauer*, Jakob Huber, Johannes Kollmann
output:
  officedown::rdocx_document:
    reference_docx: StylesTemplate.docx
  #bookdown::word_document2:
csl: template-journal-of-vegetation-science.csl
bibliography: bibliography.bib
---

@@

<mark>Max 8000 words</mark> <!--# Remove -->

@@

```{r set-up, include = FALSE}
library(knitr)
library(bookdown)
library(officedown)
library(officer)
library(tidyverse)
library(flextable)
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  dpi = 50
  )
set_flextable_defaults(
  font.family = "Times New Roman",
  font.size = 11
  )
```

@@

Mischprobe aus mehreren Plots. Measured in \< 2mm fraction <!--# Write full description + superscript and subscript in header -->

```{r table-substrate, tab.id = "substrate", tab.cap = "Substrate"}
read_csv(here::here("data", "raw", "data_raw_table_1.csv")) %>%
  slice(-1) %>%
  flextable() %>%
  bold(part = "header") %>%
  add_header_row(
    top = FALSE,
    values = read_csv(here::here("data", "raw", "data_raw_table_1.csv")) %>% slice(1)
    ) %>%
  set_table_properties(layout = "autofit", width = 1)
```
